---
author: Michael Chow
operator: local.RmdOperator
output:
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(lubridate)
library(dbplyr)
library(assertthat)

# use http v1.1, since v2 throws errors in docker
httr::set_config(httr::config(http_version = 2))

# utility funcs ----
frame_to_listcol <- function(df_col) {
  # data.frames can have columns that are data.frames. It's a bad
  # idea, so we turn them into list columns.
  split(df_col, seq(nrow(df_col)))  
}

# make sure we have a token ----
stopifnot(
  Sys.getenv("SLACK_BOT_USER_OAUTH_TOKEN") != ""
  )
```

## Fix slackr to get more than 1000 users

```{r}
library(httr)
#library(slackr)

with_locale <- function() {
  loc <- Sys.getlocale("LC_CTYPE")
  Sys.setlocale("LC_CTYPE", "C")
  Sys.setlocale("LC_CTYPE", loc)
  
  do.call("on.exit", list(substitute(Sys.setlocale("LC_CTYPE", loc))), envir = parent.frame())
}

follow_cursor <- function(crnt_data, response, func, ...) {
  cursor <- response$response_metadata$next_cursor
  if (!is.null(cursor) && cursor != "") {
    next_data <- func(cursor = cursor, ...)
    bind_rows(crnt_data, next_data)
  } else {
    crnt_data
  }
}

slackr_fixed_users <- function (bot_user_oauth_token = Sys.getenv("SLACK_BOT_USER_OAUTH_TOKEN"), cursor = "") 
{
    with_locale()

    args <- list(token = bot_user_oauth_token)
    if (cursor != "") args$cursor = cursor
    
    tmp <- httr::POST("https://slack.com/api/users.list", body = args)
    httr::stop_for_status(tmp)
    json <- jsonlite::fromJSON(httr::content(tmp, as = "text"))
    members <- json$members
    cols <- setdiff(colnames(members), c("profile", "real_name"))
    #cols_prof <- grep("image_.*", names(members$profile), value = TRUE)
    
    users <- cbind.data.frame(members[, cols], members$profile, stringsAsFactors = FALSE)
    
    follow_cursor(users, json, slackr_fixed_users)    
}

slackr_channels_fixed <- function (bot_user_oauth_token = Sys.getenv("SLACK_BOT_USER_OAUTH_TOKEN")) 
{
  with_locale()
  # NOTE: simply removed private channels from this URL
  tmp <- POST("https://slack.com/api/conversations.list?limit=500&types=public_channel", 
    body = list(token = bot_user_oauth_token))
  stop_for_status(tmp)
  jsonlite::fromJSON(content(tmp, as = "text"))$channels
}

history_slackr <- function(count,
                           ...,
                          channel=Sys.getenv("SLACK_CHANNEL"),
                          api_token=Sys.getenv("SLACK_BOT_USER_OAUTH_TOKEN")) {

  assert_that(is.string(channel))
  assert_that(is.string(api_token))


  with_locale()
  
  resp <- httr::POST(url="https://slack.com/api/conversations.history",
               body=list(token=api_token,
                         channel=channel,
                         count=count,
                         ...))
  warn_for_status(resp)

  slack_hist <- jsonlite::fromJSON(httr::content(resp, as="text"))$messages
  
  return(slack_hist)
}

slackr_channel_members <- function(
                           ...,
                          channel=Sys.getenv("SLACK_CHANNEL"),
                          api_token=Sys.getenv("SLACK_BOT_USER_OAUTH_TOKEN"),
                          cursor = "") {

  assert_that(is.string(channel))
  assert_that(is.string(api_token))

  with_locale()
  
  args <- list(token=api_token, channel=channel)
  
  if (cursor != "") args$cursor = cursor
  
  resp <- httr::POST(url="https://slack.com/api/conversations.members", body=args)
  warn_for_status(resp)
  
  json <- jsonlite::fromJSON(httr::content(resp, as="text"))

  members <- tibble(
    user = json$members
  )
  
  follow_cursor(members, json, slackr_channel_members, channel = channel, api_token = api_token)
}
```


## Fetching data

Uses the following slackr functions:

* slackr_users : get a data frame of Slack users
* slackr_channels : get a data frame of Slack channels
* slackr_groups : get a data frame of Slack groups
* slackr_history: Return message history of a Slack channel to a data.frame

```{r fetch_raw, cache = TRUE}
raw_users <-
  #slackr_users() %>%
  slackr_fixed_users() %>%
  as_tibble()# %>%
  #select(id, user_name = name)

raw_channels <-
  slackr_channels_fixed() %>%
  filter(!is_archived)

fix_empty <- function (df) {
  if (is_empty(df)) return(tibble())  
  df
}

# takes about 2 seconds per channel--so 250 * 2 = 500 seconds.
raw_messages_nested <-
  raw_channels %>%
  select(channel_id = id) %>%
  mutate(
    history = map(
      channel_id,
      slowly(~ fix_empty(history_slackr(1000, channel = .x)),  rate_delay(1.25))
    )
  )


# sanity check that dataframe columns are well-structured
# they should have same # of rows as data
# this is kind of nuts, but that's what happens when columns are data.frames
fix_raw <-
  raw_messages_nested %>%
  rowwise() %>%
  do(
    valid_subdfs = all(
      map_int(keep(.$history, ~ "data.frame" %in% class(.x)), nrow) == nrow(.$history)
    ),
    fixed = mutate_if(.$history, ~ is(., "data.frame"), frame_to_listcol),
    channel_id = .$channel_id
  ) %>%
  mutate(
    valid_subdfs = as.logical(valid_subdfs),
    channel_id = unlist(channel_id)
    )
  #{stopifnot(all(.$valid_subdfs))}
  
  
raw_messages <-
  fix_raw %>%
  unnest(fixed) %>%
  mutate(ts = as_datetime(as.numeric(ts)))

raw_channel_users <-
  raw_channels %>%
  select(channel_id = id) %>%
  mutate(
    users = map(
      channel_id,
      slowly(~  fix_empty(slackr_channel_members(channel = .x, limit = 500)),  rate_delay(1.25))
    )
  ) %>%
  unnest(users)

```

## Wrangling

Here, I just removed all the columns holding nested data. Would be quick to add useful ones as tables!

```{r wrangle}
channels <-
  raw_channels %>%
  select(
    -topic, -purpose, -previous_names, -starts_with("is_"),
    -parent_conversation, -shared_team_ids, -starts_with("pending"),
    -conversation_host_id, -unlinked, -frozen_reason
    ) %>%
  as_tibble()

channel_users <- raw_channel_users

messages <-
  raw_messages %>%
  select(
    channel_id, type, subtype, text, ts, username, bot_id, user, team, client_msg_id,
    thread_ts, reply_count, reply_users_count, latest_reply, subscribed,
    last_read, is_starred, item_type, upload_reply_to, topic,
    purpose, inviter, hidden
  )


users <-
  raw_users %>%
  select(
    id, real_name, display_name, title, team_id,deleted,updated,
    status_text, is_invited_user, bot_id, team, guest_invited_by
  )

## example of joining all data
# channels %>%
#   left_join(messages, c("name" = "channel_name")) %>%
#   left_join(users, c("user" = "id"))
```

## Create DB Tables

```{r}
cfp_create_schema("slack")
cfp_create_table(channels, "slack.channels")     # creates slack_channels table
cfp_create_table(messages, "slack.messages")
cfp_create_table(users, "slack.users")
```


## Demo of querying DB

```{r}
# example counting number of archived channels using db
#tbl(con, "channels") %>% count(is_archived)
```

```{r}
#tbl(con, "messages") %>% group_by(channel_name)
```



